
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{listings}
\usepackage{float}

% math
\usepackage{mathtools}
\usepackage{amsthm}

% math fonts
\usepackage{amssymb}
\usepackage{dsfont}

\usepackage[dvipsnames]{xcolor}
\usepackage{tikz,pgfplots}
\usepackage{pgfplotstable}

\setlength{\tabcolsep}{2pt}

\pgfplotsset{compat=newest,compat/show suggested version=false}



\setlength\parindent{0pt}

\begin{document}
We tested\footnote{Executed on the BwUniCluster 2.0 on instances with 64GB of RAM on two Cores of an Intel Xeon Gold 6230. For each method we set a time limit of 10 hours to solve all discretizations of a problem. Furthermore, we limited the maximum RAM usage to 64GB. } our methods against a classical time stepping approach. To get a fair comparison, we have implemented a Crank-Nicolson scheme which utilizes the sparseness of the space matrices via an CG method. 

For sufficient smooth examples, we were not able to beat the performance of the time stepping method due to the quadratic $L_2$ convergence of this method - in contrast to our observed linear convergence in the space-time setting. For less smooth examples, the numerical results are more diverse. We want to report some results in 2D and 3D, as the 1D case is mostly of academic nature.

\scriptsize
\section*{2D}
\subsection*{Example 1 ($u \in C^\infty$)}
\input{2D-example1}

\subsection*{Example 2 ($u \in C^0$)}
\input{2D-example2}

\subsection*{Example 3 ($u \in L_2$)}
\input{2D-example3}

\newpage
\section*{3D}
\subsection*{Example 1 ($u \in C^\infty$)}
\input{3D-example1}

\subsection*{Example 2 ($u \in C^0$)}
\input{3D-example2}

\subsection*{Example 3 ($u \in L_2$)}
\input{3D-example3}



\end{document}
